Summary Tables

### 2019-04-09 summary_tables.Rmd
Add trip prop for each case study

>>>>

## Trip proportion
Case study specific trip proportions by mode, for baseline and five scenarios

```{r trip_mode_dist = "asis", echo = F}
suppressWarnings({
  require(tidyverse)  
})

for(city in cities){
    td <- io[[city]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(p = round(n() / nrow(.) * 100, 2)) %>% spread(key = trip_mode, value = p)
    td[2:6, 1] <- rownames(scen_prop)
    print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
    cat("\n")
}

suppressWarnings({
  detach("package:tidyverse", character.only = T)
})
